A Logistic Regression Approach to CoIL Challenge 2000

### 2019-12-13 final project/Manuscript.Rmd
More work on final

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(pander)

prepare_data <- function(df){
  names(df) <- c(
    "MOSTYPE", "MAANTHUI", "MGEMOMV", "MGEMLEEF", "MOSHOOFD", "MGODRK",
    "MGODPR", "MGODOV", "MGODGE", "MRELGE", "MRELSA", "MRELOV", "MFALLEEN",
    "MFGEKIND", "MFWEKIND", "MOPLHOOG", "MOPLMIDD", "MOPLLAAG", "MBERHOOG",
    "MBERZELF", "MBERBOER", "MBERMIDD", "MBERARBG", "MBERARBO", "MSKA",
    "MSKB1", "MSKB2", "MSKC", "MSKD", "MHHUUR", "MHKOOP", "MAUT1", "MAUT2",
    "MAUT0", "MZFONDS", "MZPART", "MINKM30", "MINK3045", "MINK4575",
    "MINK7512", "MINK123M", "MINKGEM", "MKOOPKLA", "PWAPART", "PWABEDR", 
    "PWALAND", "PPERSAUT", "PBESAUT", "PMOTSCO", "PVRAAUT",  "PAANHANG",
    "PTRACTOR", "PWERKT", "PBROM", "PLEVEN", "PPERSONG", "PGEZONG",
    "PWAOREG", "PBRAND", "PZEILPL", "PPLEZIER", "PFIETS", "PINBOED",
    "PBYSTAND", "AWAPART", "AWABEDR", "AWALAND", "APERSAUT", "ABESAUT",
    "AMOTSCO", "AVRAAUT", "AAANHANG", "ATRACTOR", "AWERKT", "ABROM",
    "ALEVEN", "APERSONG", "AGEZONG", "AWAOREG",  "ABRAND", "AZEILPL",
    "APLEZIER", "AFIETS", "AINBOED", "ABYSTAND", "CARAVAN")

  MOSTYPE_labels <- c(
    "1" = "1 High Income, expensive child",
    "2" = "2 Very Important Provincials",
    "3" = "3 High status seniors",
    "4" = "4 Affluent senior apartments",
    "5" = "5 Mixed seniors",
    "6" = "6 Career and childcare",
    "7" = "7 Dinki's (double income no kids)",
    "8" = "8 Middle class families",
    "9" = "9 Modern, complete families",
    "10" = "10 Stable family",
    "11" = "11 Family starters",
    "12" = "12 Affluent young families",
    "13" = "13 Young all american family",
    "14" = "14 Junior cosmopolitan",
    "15" = "15 Senior cosmopolitans",
    "16" = "16 Students in apartments",
    "17" = "17 Fresh masters in the city",
    "18" = "18 Single youth",
    "19" = "19 Suburban youth",
    "20" = "20 Ethnically diverse",
    "21" = "21 Young urban have-nots",
    "22" = "22 Mixed apartment dwellers",
    "23" = "23 Young and rising",
    "24" = "24 Young, low educated",
    "25" = "25 Young seniors in the city",
    "26" = "26 Own home elderly",
    "27" = "27 Seniors in apartments",
    "28" = "28 Residential elderly",
    "29" = "29 Porchless seniors: no front yard",
    "30" = "30 Religious elderly singles",
    "31" = "31 Low income catholics",
    "32" = "32 Mixed seniors",
    "33" = "33 Lower class large families",
    "34" = "34 Large family, employed child",
    "35" = "35 Village families",
    "36" = "36 Couples with teens 'Married with children'",
    "37" = "37 Mixed small town dwellers",
    "38" = "38 Traditional families",
    "39" = "39 Large religous families",
    "40" = "40 Large family farms",
    "41" = "41 Mixed rurals")

  MGEMLEEF_labels <- c(
    "1" = "20-30 years",
    "2" = "30-40 years",
    "3" = "40-50 years",
    "4" = "50-60 years",
    "5" = "60-70 years",
    "6" = "70-80 years")

  MOSHOOFD_labels <- c(
    "1" = "Successful hedonists",
    "2" = "Driven Growers",
    "3" = "Average Family",
    "4" = "Career Loners",
    "5" = "Living well",
    "6" = "Cruising Seniors",
    "7" = "Retired and Religeous",
    "8" = "Family with grown ups",
    "9" = "Conservative families",
    "10" = "Farmers")

  MGODRK_labels <- c(
    "0" = "0%",
    "1" = "1 - 10%",
    "2" = "11 - 23%",
    "3" = "24 - 36%",
    "4" = "37 - 49%",
    "5" = "50 - 62%",
    "6" = "63 - 75%",
    "7" = "76 - 88%",
    "8" = "89 - 99%",
    "9" = "100%")

  PWAPART_labels <- c(
    "0" = "f 0",
    "1" = "f 1 - 49",
    "2" = "f 50 - 99",
    "3" = "f 100 - 199",
    "4" = "f 200 - 499",
    "5" = "f 500 - 999",
    "6" = "f 1000 - 4999",
    "7" = "f 5000 - 9999",
    "8" = "f 10,000 - 19,999",
    "9" = "f 20,000 - ?")

  set_to_1 <- c(12, 8, 6, 7, 1, 2, 36, 3, 37, 10, 20, 38, 11)

  df %>%
    mutate(CUSTOMER_TYPE = ifelse(MOSTYPE %in% set_to_1, 1, 0)) %>%
    mutate(CUSTOMER_TYPE = as.factor(CUSTOMER_TYPE)) %>%
    mutate(MOSTYPE = as.factor(MOSTYPE),
           MGEMLEEF = as.factor(MGEMLEEF),
           MOSHOOFD = as.factor(MOSHOOFD),
           MGODRK = as.factor(MGODRK),
           PWAPART = as.factor(PWAPART),
           CARAVAN = as.factor(CARAVAN)) %>%
    mutate(MOSTYPE = recode(MOSTYPE, !!!MOSTYPE_labels),
           MGEMLEEF = recode(MGEMLEEF, !!!MGEMLEEF_labels),
           MOSHOOFD = recode(MOSHOOFD, !!!MOSHOOFD_labels),
           MGODRK = recode(MGODRK, !!!MGODRK_labels),
           PWAPART = recode(PWAPART, !!!PWAPART_labels))
}

eval <- read.delim("data/ticeval2000.txt", header = FALSE)
temp <- read.delim("data/tictgts2000.txt", header = FALSE)
eval$CARAVAN <- temp$V1
eval <- prepare_data(eval)
df <- prepare_data(read.delim("data/ticdata2000.txt", header = FALSE))
```

@@

<!-- In the abstract, the authors should explain the major objective of the study in an objective section, explain how the study was done in a Methods section, describe the findings in a Results section, and report whether the major goal was met in a Conclusion. In general, the reader should ask, If I could not read the entire manuscript, would the abstract adequately summarize it? -->
A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.

@@

```{r, echo=FALSE}
# Recreate the chart found on page 2 of http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf
prediction_scores <- data.frame(score = c(38, 46, 53, 58, 65, 72, 74, 80, 83, 86, 91, 94, 95, 96, 97, 99, 101, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 115, 121), n = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 2, 1, 1, 1, 3, 1, 2, 2, 4, 2, 2, 2, 1, 1))
ggplot(data = prediction_scores, aes(x = score, y = n)) +
  geom_bar(stat = "identity", fill = "#377eb8") +
  xlab("Number of Correct Predictions") +
  ylab("CoIL Challenge Submissions") +
  xlim(37, 122) +
  scale_fill_brewer(palette = "Set1")
```

@@

@@

  Name = c("MOSTYPE", "MAANTHUI", "MGEMOMV", "MGEMLEEF", "MOSHOOFD", "MGODRK",

@@

           "ABYSTAND", "CARAVAN"),
  Description = c("Customer Subtype", "Number of houses", "Avg size household",

@@

                  "Number of mobile home policy"))
pander(data_dictionary)

@@

@@

<code>
```{r, null_prefix = TRUE, comment=NA, echo=FALSE}
conn <- file("CoIL.r", open = "r")
lines <- readLines(conn)
n_lines <- length(lines)
for (i in 1:n_lines) {
  cat(lines[i], "\n")
}
close(conn)
```
</code>

>>>>

```{r echo=FALSE, message=FALSE}
source("CoIL.R")
library(pander)
knitr::opts_chunk$set(comment = NA)
```

@@

<!-- In the abstract, the authors should explain the major objective of the study in an objective section, explain how the study was done in a Methods section, describe the findings in a Results section, and report whether the major goal was met in a Conclusion. In general, the reader should ask, If I could not read the entire manuscript, would the abstract adequately summarize it? -->
A logistic regression based solution to the CoIL Challenge 2000 is described in this paper. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics. Models were trained on over sampled data.  The model out preformed other's attemps.

@@

```{r, echo=FALSE}
# Similar the chart found on page 2 of http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf
prediction_scores <- data.frame(score = c(38, 46, 53, 58, 65, 72, 74, 80, 83, 86, 91, 94, 95, 96, 97, 99, 101, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 115, 121), n = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 2, 1, 1, 1, 3, 1, 2, 2, 4, 2, 2, 2, 1, 1))
ggplot(data = prediction_scores, aes(x = score, y = n)) +
  geom_bar(stat = "identity", fill = "#377eb8") +
  xlab("Number of Correct Predictions") +
  ylab(element_blank()) + 
  xlim(37, 240) +
  annotate("text", x = 65, y = 4, label = "Previous Researchers") +
  geom_vline(xintercept = 238, color = "#e41a1c", linetype="dashed") +
  annotate("text", x = 220, y = 4, label = "Maximum") +
  geom_vline(xintercept = final_model$correct, color = "#4daf4a") +
  annotate("text", x = final_model$correct - 20, y = 4, label = "Our Model") +
  ggtitle("Number of Customers Correctly Predicted")
```

@@

## Correlation Coefficients for Variables of Interest
```{r, echo=FALSE}
vars <- c("CARAVAN", "PPERSAUT", "PBRAND", "APERSAUT", "LIKELY_CUSTOMERS")
temp <- up_train %>%
  mutate(CARAVAN = as.numeric(as.character(CARAVAN)),
         LIKELY_CUSTOMERS = as.numeric(as.character(LIKELY_CUSTOMERS)))
temp <- temp[vars]

pander(cor(temp[vars], temp[vars]))
```

@@

  Name = c("CARAVAN", "MOSTYPE", "MAANTHUI", "MGEMOMV", "MGEMLEEF", "MOSHOOFD", "MGODRK",

@@

           "ABYSTAND", "LIKELY_CUSTOMERS"),
  Description = c("Number of mobile home policy",
                  "Customer Subtype", "Number of houses", "Avg size household",

@@

                  "MOSTYPE = 12, 8, 6, 7, 1, 2, 36, 3, 37, 10, 20, 38, or 11"))
temp <- data_dictionary[data_dictionary$Name %in% vars,]
row.names(temp) <- NULL
pander(temp)

@@

## Confusion Matrix and Statistics for our Model

```{r, echo=FALSE}
final_model$cm
```

@@

```{r, null_prefix = TRUE, comment=NA, echo=FALSE}
conn <- file("CoIL.r", open = "r")
lines <- readLines(conn)
n_lines <- length(lines)
for (i in 1:n_lines) {
  cat(lines[i], "\n")
}
close(conn)
```
